---
title: "Interesting Forecasting Applications with R"
author: "Huseyin Sengun - IE360 - Spring 2021"
---
```{r,echo=FALSE,results="hide"}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
```

```{r,echo=FALSE,eval=FALSE}
rmarkdown::render("/home/baydogan/Courses/IE360/Guidelines/example_homework_0.Rmd",output_format="pdf_document")
rmarkdown::render("/home/baydogan/Courses/IE360/Guidelines/example_homework_0.Rmd",output_format="html_document")
```

1. [Time series forecasting using ARIMA models](https://blogs.oracle.com/datascience/introduction-to-forecasting-with-arima-in-r)

    This example is important because it introduces the forecasting methodology using ARIMA models in R. The steps are 1-)Examine your data 2-)Decompose your data 3-)Stationarity 4-)Autocorrelations and choosing model order 5-)Fit an ARIMA model 6-)Evaluate and iterate

2. [Forecasting with R - Trends and Seasonality](https://towardsdatascience.com/forecasting-with-r-trends-and-seasonality-def24280e71f)
  
    This example is important because it shows how essential it is to learn basics.

3.  [Energy Consumption - Time Series Forecasting](https://www.kaggle.com/apoorvabhide/energy-consumption-time-series-forecasting-in-r) 

     This example is important because it's a Kaggle project and shows everything from scratch to final.
     

4. [Web Traffic Time Series Forecasting](https://github.com/Arturus/kaggle-web-traffic/blob/master/how_it_works.md)    

     This project is taken from a real Kaggle competition, given by Google. The solution on the link is the winner of the competition, although codes are written in Python. 


5. [Multiple Time Series Forecast & Demand Pattern Classification](https://towardsdatascience.com/multiple-time-series-forecast-demand-pattern-classification-using-r-part-1-31601158d33b)    

    
