---
title: "Project Report"

output: html_document
---

```{r,echo=FALSE,results="hide"}
library(knitr)
library(formatR)


opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
```
```{r,echo=FALSE,eval=FALSE}
rmarkdown::render("C:/Users/admin/Documents/GitHub/spring21-huseyinsengn/files/Project/Project/projectson.Rmd",output_format="pdf_document")
rmarkdown::render("C:/Users/admin/Documents/GitHub/spring21-huseyinsengn/files/Project/Project/projectson.Rmd",output_format="html_document")
```

# IE 360 PROJECT REPORT

## Description

Trendyol is Turkey’s leading e-commerce platform and has become Turkey’s most valuable company with its recent fundraising round and continues to grow rapidly with its vision of becoming all-in-app.

In this project, we are provided the data of 9 different products and we are asked to build models for forecasting the next-day sales of these 9 products. The data we provided starts from 30 May 2020 and lasts until the end of May 2021. In the competition period, each team made submissions every day and has gained points depending on how accurate their predictions were. 

The data consists of different attributes for each of the products which are “price”, “sold_count”, “visit_count”, “basket_count”, favored_count”, “category_sold”, “category_visits”, “category_basket”, “category_favored”, “category_brand_sold” and “ty_visits”. We have used the forecasting methods we’ve learned in the lectures, by using different methods and comparing the forecasting models we’ve created, we tried to achieve the best forecasting models for each of the products. 

There are 9 product types in the data: 
*ALTINYILDIZ CLASSICS Mont
*TRENDYOLMİLLA Bikini Üstü
*TRENDYOLMİLLA Bikini Üstü
*TRENDYOLMİLLA Tayt
*Xiaomi Bluetooth Kulaklık
*Fakir Dik Süpürge
*La Roche Posay Yüz Temizleyici
*Sleepy Bebek Islak Mendil
*Oral-B Şarj Edilebilir Diş Fırçası



## Approach

Before the model selection, we analyze the data for features of products’ data.After analysis of data, we start building linear regression models with proper parameters that we eliminate step by step. Then, we make effort to finding parameters for arima models.For best arima model, we check statistical values.After elimination processes for these two different models, we are able to test overall performance of these two models to find the best model for forecasting period.With model that has better statistical ,we forecast for next day during competition period.


## RESULTS


## Product1




predict(product1_reg,data.frame(price=449.985,basket_count=basket_count_model_forecast[16],category_basket=category_basket_model_forecast[16],category_favored=category_favored_model_forecast[16],ty_visits=ty_visits_model_forecast[16]))


->3.389179 

## Product2




predict(product2_reg,data.frame(basket_count=basket_count_model_forecast[16],favored_count=favored_count_model_forecast[16],category_sold=category_sold_model_forecast[16],category_basket=category_basket_model_forecast[16], category_favored=category_favored_model_forecast[16],category_brand_sold=category_brand_sold_model_forecast[16], ty_visits=ty_visits_model_forecast[16]))


->99.87471

## Product3





predict(product3_reg,data.frame(basket_count=basket_count_model_forecast[16],favored_count=favored_count_model_forecast[16],category_sold=category_sold_model_forecast[16],category_visits=category_visits_model_forecast[16],category_basket=category_basket_model_forecast[16], category_favored=category_favored_model_forecast[16],category_brand_sold=category_brand_sold_model_forecast[16]))

->48.9182

## Product4 



forecast_Log<-predict(lm_model2_1,data.frame(month=as.factor(6) ,price=price_model_forecast[1],category_sold=cat_fcast[1],lag_1=lag1_fcast[1],lag_2=lag_2_model_forecast[1],outlier_great=outlier_model_forecast[1]))

fcast<-exp(forecast_Log)
fcast


->541.3558 


## Product5



forecast_log<-predict(lm_model3_2,data.frame(month=as.factor(6) ,price=price_model_forecast[1],trend=373,favored_count=fav_fcast[1],category_sold=cat_ffcast[1],category_brand_sold=brand_model_forecast[1],lag_1=lag1_fcast[1],lag_2=lag2_fcast[1],category_favored=cat_fav_model_forecast[1],outlier_great=outlier_model_forecast[1],weeks=21))
fcast2<-exp(forecast_log)
fcast2

->475.5609 

## Product6




forecast_Log<-predict(lm_model2_3,data.frame(month=as.factor(6) ,price=price_model_forecast[1],trend=373,favored_count=fav_fcast[1],category_sold=cat_fcast[1],category_brand_sold=brand_fcast[1],lag_1=lag1_fcast[1],lag_2=lag2_fcast[1],outlier_small=small_fcast[1]))
fcast3<-exp(forecast_Log)
fcast3

->29.69554 

## Product 7




predict(lmIslakMendil,data.frame(basket_count=basket_count_model_forecast,category_sold=category_sold_model_forecast,category_favored=category_favored_model_forecast,category_visits=category_visits_model_forecast,category_brand_sold=category_brand_sold_model_forecast))

->430.6934 

## Product 8




predict(lmYuzTemizleyici,data.frame(price=price_model_forecast,visit_count=visit_count_model_forecast, basket_count=basket_count_model_forecast,favored_count=favored_count_model_forecast,category_sold=category_sold_model_forecast,category_basket=category_basket_model_forecast, category_favored=category_favored_model_forecast,category_brand_sold=category_brand_sold_model_forecast,ty_visits=ty_visits_model_forecast,  month= as.factor(6), trend=0, day=as.factor(3), Residual=Residual_model_forecast, lag_1=lag_1_model_forecast))

->80.82597

## Product 9



predict(lmDisFircasi,data.frame(basket_count=basket_count_model_forecast,favored_count=favored_count_model_forecast,category_sold=category_sold_model_forecast,category_favored=category_favored_model_forecast,category_brand_sold=category_brand_sold_model_forecast))


->143.5191 

## Conclusion and Future Work

As a project of IE360 Statistical Forecasting and Time Series course, we had a chance to challenge the knowledge we gain during the term in real life. Creating forecasting models from scratch, developing the models we created during the competition period, researching the related documents on the Internet, and having a chance to dealing with a real-life challenge were beneficial tasks for each team member to challenge and develop ourselves. 

However, the biggest challenge we’ve faced during the project is that there were lots of NA values in the product data. These missing values made the model building and developing phases more complex for us and sometimes although we had the theoretical-statistical knowledge, dealing with the coding and syntax problems made the process harder and more complex for us. We’ve researched the causes and solved the coding errors when we face these kinds of problems.

We’ve deeply analyzed each product data and manipulated it in a way to make the data more understandable and meaningful. Then, we start building models step by step. After making lots of effort in building the models, we’ve chosen the models that give the best results during the test periods by checking the statistical values. On the .rmd file, we’ve added comments about our model selection&developing processes. 

It was hard to use external factors in the models such as special, unexpected discounts, or any other external factors that might have an influence on the sold quantities of the products. For example, during the competition period, Trendyol has “Babalar Günü” campaigns and we see the effect of the external factors.

As future work, more detailed information about the sales and customers could be used while forecasting. Companies like Trendyol use customer segmentation methods and other data science algorithms very well. Therefore, these methods could be added to the forecasting models. Although it’s hard to predict the external factors and add them to the model, we see the importance of these factors on predictions. One external factor that could be added to the forecasting models is that the price of the same product on other e-commerce platforms such as Amazon, Hepsiburada, or the brand’s own web page. These price differences will probably have an important effect on the daily sales of Trendyol.

## Code

[Rmd file for project](https://github.com/BU-IE-360/spring21-onurcanaydinn/blob/master/files/project.Rmd)

## Team members

Onur Can Aydın
Hüseyin Şengün
Mehmet Akif Taşçıoğlu

